---
author: "Paul Victor"
output: pdf_document
title: "Salary Analysis"
---

```{r functions, include=F}
### Dummy Variable gen
dumvar <- function(col, col_nm){
  ### Generates dummy variables and drops the one level/column that 
  ### has the fewest number of occurances.
  #
  ### Args
  #   col = dataframe of column(s) to convert do dummy variables 
  #   col_nm = Original name of columns
  #
  ### Output 
  #   Dataframe of dummy variables with new names.
  
  dummy1 <- dummy.code(col) %>% as.data.frame
  colnames(dummy1) <- paste0("I.", col_nm, '.', colnames(dummy1))
  com_set <- unique(col)
  com_set <- paste0("I.", col_nm, '.', com_set)
  min_com_set <- apply(select(dummy1, com_set), 2, sum) %>% which.min %>% names
  
  if (length(com_set) == 2) {
    colnm <- names(dummy1)[-which(names(dummy1)==min_com_set)]
    dummy1 <- dummy1[, -which(names(dummy1) == min_com_set)]
    dummy1 <- data.frame(dummy1)
    colnames(dummy1) <- colnm
  } else {
    dummy1 <- dummy1[,-grep(min_com_set, colnames(dummy1), fixed = T)]
  }

  return(dummy1)
}



### Collinearity/Correlation
col_cor <- function(df, p = 0.75){
  ### Calculates correlation of all columns.
  ### Filters to only column relationships with a correlation >= 0.75
  #
  ### Args
  #   df = Dataframe of columns to test correlation
  #   p = % of correlation (R2) to filter to
  #
  ### Output
  #   Dataframe of pairs of columns & their correlation
  
  cor_col <- df %>%
  cor() %>%
  melt %>%
  filter(abs(value) > p & Var1 != Var2) %>%
  arrange(value)

  ### Concatenate and sort Var1 & Var2 to later remove any duplicates
  cor_col$concat <- paste(cor_col$Var1, cor_col$Var2)
  cor_col$concat <- sapply(lapply(strsplit(cor_col[,4], " "), sort),paste,collapse = " ")
  
  cor_col <- cor_col[duplicated(cor_col$concat) == F, ]
  
  cor_col <- cor_col[,-4]
  return(cor_col)
}



### Partition Data into Train, Validation, & Test
part_data <- function(df, col, dc = c(""), tr = 0.6, va = 0.2, te = 0.2, dummy = F){
    ### This function partitions your df into train, test & validation.
    ### It also will apply a row index column for future reference.
    #
    ### Args
    #   df = Dataframe of response & predictors
    #   col = Columns to include in model
    #   dc = Column to Drop
    #   tr = % training data partition
    #   va = % validation data partition
    #   te = % test data partition
    #######################################################################
    ### Function to Parittion train, validatin, test
    g = function(df, spec, seed){
      set.seed(seed)
      sample(cut(
      seq(nrow(df)),
      nrow(df)*cumsum(c(0,spec)),
      labels = names(spec)
      ))}
  
    ctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 10)
    spec = c(train = tr, test = va, validate = te)
    stoch_spec <- c(train = tr, validate = te + va)

    # drop_col <- c('a1_spey_d_perc')
    drop_col <- dc
    # df_19_a1_km3 <- cbind(dfy19ea1$TOTAL_PASS_PERC, df_19_a1_km3)
    # colnames(df_19_a1_km3)[1] <- 'TOTAL_PASS_PERC'

    if (dummy){
      rf_col = c(col, 
                 dummy_var,
                 'index')
    } else{
      rf_col = c(col, 
                 'index')
    }
    # rf_col = c(tested_cols_perc, 'index')
    df$index = as.integer(row.names(df))
    res = split(df[,rf_col], g(df, spec, 1))

    ### Define data
    train_df <- res$train
    train_i <- train_df$index
    # train_df <- select(train_df, -index)
    val_df <- res$validate
    val_i <- val_df$index
    # val_df <- select(val_df, -index)
    test_df <- res$test
    test_i <- test_df$index
    # test_df <- select(test_df, -index)

    return(list(train_df, val_df, test_df))
}

### Execute powerTransform through all columns
transf <- function(df){
  # Calculates BoxCox lambda value
  #
  ### Args
  #   df = data frame of columns (No Negatives)
  # 
  ### Output
  #   df = dataframe with lambda value for each column
  
  trans <- lapply(df, function(x) powerTransform(x + .001)$lambda) %>% unlist
  names(trans) <- gsub('\\..*', '', names(trans))
  return(trans)
}
```

```{r libraries/settings}
options(scipen = 9999)

library(dplyr)
library(ggplot2)
library(gridExtra)
library(stringr)
library(psych)
library(data.table)
library(caret)
library(car)
library(parallel)
library(doParallel)
librar(explora)
library(DataExplorer)
```

# Problem 
From the data provided by this company the question we want to answer is, what variables are key in predicting current salary?  How accurate can we predict current salary based on a subset number of predictors?

# Process


# Read in Data
```{r read_data}
nb <- read.csv('NewBankData.csv')

nb$index <- seq_len(nrow(nb))

nb$traineeprogram <- str_replace_all(nb$traineeprogram, 'O', '0') %>% as.integer()

```

# Data Processing
```{r}
### Drop one bad row of missing experience data point.
nb <- nb[nb$experience != -1, ]
```


# DEA
## Missing Data
```{r}
plot_missing(nb)
```


## Response & Predictors Distribution
```{r}
ggplot(nb, aes(x = currentsalary)) + 
  geom_histogram(color = 'black', fill = 'lightblue', bins = 30) +
  labs(x = 'Current Salary', y = 'Frequency') +
  ggtitle('Current Salary Distribution') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.title.x = element_text(face = 'bold'),
        axis.title.y = element_text(face = 'bold'))

g1 <- ggplot(nb, aes(x = education)) + 
  geom_histogram(color = 'black', fill = 'lightblue', bins = 30) +
  labs(x = 'Education', y = 'Frequency') +
  ggtitle('Education Distribution') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.title.x = element_text(face = 'bold'),
        axis.title.y = element_text(face = 'bold'))

g2 <- ggplot(nb, aes(x = experience)) + 
  geom_histogram(color = 'black', fill = 'lightblue', bins = 30) +
  labs(x = 'Experience', y = 'Frequency') +
  ggtitle('Experience Distribution') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.title.x = element_text(face = 'bold'),
        axis.title.y = element_text(face = 'bold'))

g3 <- ggplot(nb, aes(x = seniority)) + 
  geom_histogram(color = 'black', fill = 'lightblue', bins = 30) +
  labs(x = 'Seniority', y = 'Frequency') +
  ggtitle('Seniority Distribution') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.title.x = element_text(face = 'bold'),
        axis.title.y = element_text(face = 'bold'))

g4 <- ggplot(nb, aes(x = startingsalary)) + 
  geom_histogram(color = 'black', fill = 'lightblue', bins = 30) +
  labs(x = 'Starting Salary', y = 'Frequency') +
  ggtitle('Starting Salary Distribution') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.title.x = element_text(face = 'bold'),
        axis.title.y = element_text(face = 'bold'))

grid.arrange(g1,g2,g3, g4, nrow = 2)
  
```

## Job Category & Salary
```{r}
g1 <- ggplot(nb) +
  geom_boxplot(aes(x = jobcategory, y = startingsalary, fill = jobcategory)) +
  ggtitle('Job Cateogry vs. Starting Salary') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))

g2 <- ggplot(nb) +
  geom_boxplot(aes(x = jobcategory, y = currentsalary, fill = jobcategory)) +
  ggtitle('Job Cateogry vs. Current Salary') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))


g3 <- ggplot(nb) +
  geom_boxplot(aes(x = jobcategory, y = (currentsalary - startingsalary), fill = jobcategory)) +
  ggtitle('Job Cateogry vs. Delta Salary') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))

grid.arrange(g1,g2,g3, nrow = 1)
```

## Job Category & Experience
```{r}
### Plot experience by Job Cateogry
ggplot(nb, aes(x = jobcategory, y = experience, fill = jobcategory)) +
  geom_boxplot() 
```

## Job Category & Education
```{r}
ggplot(nb, aes(x = jobcategory, y = education, fill = jobcategory)) +
  geom_boxplot()  +
  ggtitle('Job Cateogry vs. Education') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))

```

Majority of Admin, Security, & Tellers have no more than 14 years of education (No more than Associates Degree).

## Gender & Salary
```{r fig.width = 10, fig.asp = 0.55, fig.align = 'center'}
g1 <- ggplot(nb) +
  geom_boxplot(aes(x = sex, y = startingsalary, fill = sex)) +
  ggtitle('Job Cateogry vs. Starting Salary') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))

g2 <- ggplot(nb) +
  geom_boxplot(aes(x = sex, y = currentsalary, fill = sex)) +
  ggtitle('Job Cateogry vs. Current Salary') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))


g3 <- ggplot(nb) +
  geom_boxplot(aes(x = sex, y = (currentsalary - startingsalary), fill = sex)) +
  ggtitle('Job Cateogry vs. Delta Salary') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))

grid.arrange(g1,g2,g3, nrow = 1)
```

## Gender & Experience
```{r}
### Plot experience by Job Cateogry
ggplot(nb, aes(x = sex, y = experience, fill = sex)) +
  geom_boxplot()  +
  ggtitle('Gender vs. Experience') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))
```

## Gender & Education
```{r}
ggplot(nb, aes(x = sex, y = education, fill = sex)) +
  geom_boxplot()  +
  ggtitle('Gender vs. Education') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))

```

Majority of Admin, Security, & Tellers have no more than 14 years of education (No more than Associates Degree).

## Compare Gender Salary with similar education
```{r}
ggplot(nb, aes(x = as.character(education), y = startingsalary, fill = sex)) +
  geom_bar(stat = "identity", position = position_dodge()) 
```

## Education vs. Job Category
```{r fig.width = 10, fig.asp = 0.55, fig.align = 'center'}
lbl = with(nb[nb$education <= 16,], paste0(jobcategory, sex))

g1 <- ggplot(filter(nb, education <= 16), aes(x = as.character(education), y = startingsalary, fill = lbl, label = lbl)) +
  geom_boxplot() + 
  labs(x = 'education') 
g2 <- ggplot(filter(nb, education <= 16), aes(x = as.character(education), y = currentsalary, fill = lbl, label = lbl)) +
  geom_boxplot() + 
  labs(x = 'education')
g3 <- ggplot(filter(nb, education <= 16), aes(x = as.character(education), fill = lbl)) +
  geom_histogram(stat = 'count', position = position_dodge()) + 
  labs(x = 'education')
# ggplot(filter(nb, education <= 16), aes(x = as.character(education), fill = lbl)) +
#   geom_violin(stat = 'count', position = position_dodge())

g1
g2
g3
```

# Feature Engineer
```{r}
nb <- nb %>% 
  mutate(salaryincrease = currentsalary - startingsalary)
```


## Correlation Analysis
```{r}
cor_tbl <- col_cor(nb)

# Customize upper panel
upper.panel<-function(x, y){
  points(x,y, pch = 19)
}
# Correlation panel
panel.cor <- function(x, y){
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- round(cor(x, y), digits=2)
    txt <- paste0("R = ", r)
    cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor * r)
}
## put histograms on the diagonal
panel.hist <- function(x, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(usr[1:2], 0, 1.5) )
    h <- hist(x, plot = FALSE)
    breaks <- h$breaks; nB <- length(breaks)
    y <- h$counts; y <- y/max(y)
    rect(breaks[-nB], 0, breaks[-1], y, col = "cyan", ...)
}
pairs(currentsalary ~ age + sex + education + experience + seniority + jobcategory + traineeprogram + startingsalary, data = nb, lower.panel = panel.cor, upper.panel = upper.panel, diag.panel = panel.hist)
```

Age & experience have a high correlation.  I dropped age as I was more interested in experience no matter what age you entered the company.

## Dummy Variables
```{r}
ogdumv <- c('jobcategory', 'sex', 'traineeprogram')
dum1 <- dumvar(nb$jobcategory, 'jobcategory')
dum2 <- dumvar(nb$sex, 'sex')
dum3 <- dumvar(nb$traineeprogram, 'traineeprogram')

dumall <- cbind(dum1, dum2, dum3)
dummy_var <- colnames(dumall)

nb <- nb %>% 
  select(-ogdumv)

nb <- cbind(nb, dumall)

nbmc <- nb %>% 
  select(-age)
```


# Modeling Prep
```{r include=FALSE}
### Drop row with missing value from experience
nbmc <- nbmc %>% 
  filter(experience != -1)

allvar <- c("education", "age","experience", "seniority", "I.jobcategory.Admin", 
"I.jobcategory.Executive", "I.jobcategory.IT", "I.jobcategory.Management", 
"I.jobcategory.Security", "I.jobcategory.Teller", "I.sex.M", 
"I.traineeprogram.1")

mlvar <- c("education", "experience", "seniority", "I.jobcategory.Admin", 
"I.jobcategory.Executive", "I.jobcategory.IT", "I.jobcategory.Management", 
"I.jobcategory.Security", "I.jobcategory.Teller", "I.sex.M", 
"I.traineeprogram.1")

mlvary_nm <- 'currentsalary'
mlvary <- nbmc$currentsalary
```

## Transformations
```{r}
df_trans <- transf(nbmc[, c('currentsalary', 'startingsalary','education', 'experience', 'seniority')])
df_trans
```

### Plot Transformation
```{r}
ggplot(nb, aes(x = log(currentsalary))) + 
  geom_histogram(color = 'black', fill = 'lightblue', bins = 30) +
  labs(x = 'Log Current Salary', y = 'Frequency') +
  ggtitle('Log Current Salary Distribution') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.title.x = element_text(face = 'bold'),
        axis.title.y = element_text(face = 'bold'))
```


# Partition Data
```{r}
pd <- nbmc %>% 
  select(-employeeID)

df_l <- part_data(pd, c(mlvary_nm, mlvar))
train_df_mc <- df_l[[1]]
val_df_mc <- df_l[[2]]
test_df_mc <- df_l[[3]]


df_l <- part_data(nb, c(mlvary_nm, allvar))
train_df <- df_l[[1]]
val_df <- df_l[[2]]
test_df <- df_l[[3]]
```

## OLS
```{r}
m1_lm_all <- lm(log(currentsalary) ~ (. - index)^2 , train_df_mc)

n <- length(m1_lm_all$residuals)
m1_lm <- step(m1_lm_all, direction = "backward", data = train_df_mc, k=log(n), trace = 0)

postResample(exp(predict(m1_lm)), train_df_mc$currentsalary)
```

### OLS Test
```{r}
100/nrow(test_df_mc) * sum(abs((test_df_mc$currentsalary - exp(predict(m1_lm, test_df_mc)))/test_df_mc$currentsalary))
1/nrow(test_df_mc) * sum(abs((test_df_mc$currentsalary-exp(predict(m1_lm, test_df_mc)))))


actual_df <- data.frame(val = test_df_mc$currentsalary, type = "actual", index = test_df_mc$index)
pred_df <- data.frame(val = exp(predict(m1_lm, test_df_mc)), type = "test", index = "0")
mast_df <- rbind(actual_df, pred_df)
mast_df$OBS <- rep(seq(1,nrow(actual_df)), 2)
mast_df <- merge(mast_df,nb, by = c('index'), all.x = TRUE)
mast_df <- mast_df %>% 
  group_by(OBS) %>% 
  mutate(MAPE = 100*(abs(val[type == "actual"]-val[type=="test"]))/(val[type=="actual"]),
         ACTUAL = val[type == 'actual'],
         PREDICT = val[type == 'test']) %>% 
  dplyr::ungroup() %>% 
  as.data.frame

mast_df <- arrange(mast_df, type, val, OBS)
order_x <- mast_df$OBS
order_x <- factor(order_x, levels = unique(order_x))

lbl <- paste(mast_df$dname, round(mast_df$MAPE,2), sep = "\n")

### Residual Plot
ggplot(mast_df)+
  geom_line(aes(group = OBS, x = as.factor(order_x), y = val), alpha = 0.2, size = 1.1) +
  geom_point(aes(x = as.factor(order_x), y = val, col = type, label = lbl), size = 2.5) +
  ggtitle("Test Resdiual Plot - OLS") +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank())+
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE)) +
  ylab("Current Salary") +
  xlab("Index")

```

## Elastic Net
```{r}
m1_lm_all <- lm(log(currentsalary) ~ ., train_df_mc)

n <- length(m1_lm_all$residuals)
m1_lm <- step(m1_lm_all, direction = "backward", data = train_df_mc, k=log(n), trace = 0)

postResample(exp(predict(m1_lm)), train_df_mc$currentsalary)
```
### Elastic Net Test
```{r}
100/nrow(test_df_mc) * sum(abs((test_df_mc$currentsalary - exp(predict(m1_lm, test_df_mc)))/test_df_mc$currentsalary))
1/nrow(test_df_mc) * sum(abs((test_df_mc$currentsalary-exp(predict(m1_lm, test_df_mc)))))


actual_df <- data.frame(val = test_df_mc$currentsalary, type = "actual", index = test_df_mc$index)
pred_df <- data.frame(val = exp(predict(m1_lm, test_df_mc)), type = "test", index = "0")
mast_df <- rbind(actual_df, pred_df)
mast_df$OBS <- rep(seq(1,nrow(actual_df)), 2)
mast_df <- merge(mast_df,nb, by = c('index'), all.x = TRUE)
mast_df <- mast_df %>% 
  group_by(OBS) %>% 
  mutate(MAPE = 100*(abs(val[type == "actual"]-val[type=="test"]))/(val[type=="actual"]),
         ACTUAL = val[type == 'actual'],
         PREDICT = val[type == 'test']) %>% 
  dplyr::ungroup() %>% 
  as.data.frame

mast_df <- arrange(mast_df, type, val, OBS)
order_x <- mast_df$OBS
order_x <- factor(order_x, levels = unique(order_x))

lbl <- paste(mast_df$dname, round(mast_df$MAPE,2), sep = "\n")

### Residual Plot
ggplot(mast_df)+
  geom_line(aes(group = OBS, x = as.factor(order_x), y = val), alpha = 0.2, size = 1.1) +
  geom_point(aes(x = as.factor(order_x), y = val, col = type, label = lbl), size = 2.5) +
  ggtitle("Test Resdiual Plot - OLS") +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank())+
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE)) +
  ylab("Current Salary") +
  xlab("Index")

```

## Random Forest
```{r eval=FALSE, include=FALSE}
ctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 10)

cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
registerDoParallel(cluster)
m1_rf <- train(log(currentsalary) ~ . - index,
          data = train_df,
          method = 'rf',
          metric = 'MAE',
          trControl = ctrl,
          preProcess = c('center', 'scale', "BoxCox"),
          importance = T,
          tuneLength = 5L)
stopCluster(cluster)

rf_pred <- exp(predict(m1_rf, val_df))

100/nrow(val_df) * sum(abs((val_df$currentsalary-rf_pred)/val_df$currentsalary))
1/nrow(val_df)*sum(abs((val_df$currentsalary - rf_pred)))

postResample(rf_pred, val_df$currentsalary)
plot(val_df$currentsalary, rf_pred)

```
### Random Forest Test
```{r eval=FALSE, include=FALSE}
100/nrow(test_df) * sum(abs((test_df$currentsalary - exp(predict(m1_rf, test_df)))/test_df$currentsalary))
1/nrow(test_df) * sum(abs((test_df$currentsalary-exp(predict(m1_rf, test_df)))))

rf_test_pred <- predict(m1_rf, test_df)
postResample(rf_test_pred, test_df$currentsalary)

actual_df <- data.frame(val = test_df$currentsalary, type = "actual", index = test_df$index)
pred_df <- data.frame(val = exp(predict(m1_rf, test_df)), type = "test", index = "0")
mast_df <- rbind(actual_df, pred_df)
mast_df$OBS <- rep(seq(1,nrow(actual_df)), 2)
mast_df <- merge(mast_df,nb, by = c('index'), all.x = TRUE)
mast_df <- mast_df %>% 
  group_by(OBS) %>% 
  mutate(MAPE = 100*(abs(val[type == "actual"]-val[type=="test"]))/(val[type=="actual"]),
         ACTUAL = val[type == 'actual'],
         PREDICT = val[type == 'test']) %>% 
  dplyr::ungroup() %>% 
  as.data.frame

mast_df <- arrange(mast_df, type, val, OBS)
order_x <- mast_df$OBS
order_x <- factor(order_x, levels = unique(order_x))

lbl <- paste(mast_df$employeeID, round(mast_df$MAPE,2), sep = "\n")

### Residual Plot
ggplot(mast_df)+
  geom_line(aes(group = OBS, x = as.factor(order_x), y = val), alpha = 0.2, size = 1.1) +
  geom_point(aes(x = as.factor(order_x), y = val, col = type, label = lbl), size = 2.5) +
  ggtitle("Test Resdiual Plot - RF") +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank())+
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE)) +
  ylab("Current Salary") +
  xlab("Index")

```

## XGBoost
```{r eval=FALSE, include=FALSE}
ctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 10)

cluster <- makeCluster(detectCores() - 1) # convention to leave 1 core for OS
registerDoParallel(cluster)
m1_xgb <- train(log(currentsalary) ~ . - index,
          data = train_df,
          method = 'xgbTree',
          metric = 'MAE',
          trControl = ctrl,
          preProcess = c('center', 'scale', "BoxCox"),
          importance = T,
          tuneLength = 5L)
stopCluster(cluster)

rf_pred <- exp(predict(m1_xgb, val_df))

100/nrow(val_df) * sum(abs((val_df$currentsalary-rf_pred)/val_df$currentsalary))
1/nrow(val_df)*sum(abs((val_df$currentsalary - rf_pred)))

postResample(rf_pred, val_df$currentsalary)
plot(val_df$currentsalary, rf_pred)

```
### XGBoost Test
```{r eval=FALSE, include=FALSE}
100/nrow(test_df) * sum(abs((test_df$currentsalary - exp(predict(m1_xgb, test_df)))/test_df$currentsalary))
1/nrow(test_df) * sum(abs((test_df$currentsalary-exp(predict(m1_xgb, test_df)))))

rf_test_pred <- predict(m1_xgb, test_df)
postResample(rf_test_pred, test_df$currentsalary)

actual_df <- data.frame(val = test_df$currentsalary, type = "actual", index = test_df$index)
pred_df <- data.frame(val = exp(predict(m1_xgb, test_df)), type = "test", index = "0")
mast_df <- rbind(actual_df, pred_df)
mast_df$OBS <- rep(seq(1,nrow(actual_df)), 2)
mast_df <- merge(mast_df,nb, by = c('index'), all.x = TRUE)
mast_df <- mast_df %>% 
  group_by(OBS) %>% 
  mutate(MAPE = 100*(abs(val[type == "actual"]-val[type=="test"]))/(val[type=="actual"]),
         ACTUAL = val[type == 'actual'],
         PREDICT = val[type == 'test']) %>% 
  dplyr::ungroup() %>% 
  as.data.frame

mast_df <- arrange(mast_df, type, val, OBS)
order_x <- mast_df$OBS
order_x <- factor(order_x, levels = unique(order_x))

lbl <- paste(mast_df$type, mast_df$OBS, mast_df$employeeID, round(mast_df$MAPE,2), sep = "\n")

### Residual Plot
ggplot(mast_df) +
  geom_line(aes(group = OBS, x = as.factor(order_x), y = val), alpha = 0.2, size = 1.1) +
  geom_point(aes(x = as.factor(order_x), y = val, col = type, label = lbl), size = 2.5) +
  ggtitle("Test Resdiual Plot - RF") +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank())+
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE)) +
  ylab("Current Salary") +
  xlab("Index")

ggplot(filter(mast_df, type == 'actual')) +
  geom_point(aes(x = as.factor(order_x[1:(length(order_x)/2)]), y = (PREDICT - ACTUAL), label = lbl[1:(length(lbl)/2)], color = education)) +
  geom_abline(intercept = 0) +
  scale_color_gradient2(colours = terrain.colors(10))

```
